The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-10-07 manuscript/manuscript.tex
Finish udpate the paper based on the referee report!!!

\usepackage{times}
\usepackage{natbib}
\usepackage[backref,breaklinks,colorlinks,citecolor=cyan]{hyperref} 
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{bm}
%\usepackage{deluxetable}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}
\usepackage[caption=false]{subfig}

@@

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.5\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs. \ding{TBC: However, an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $+6.8$ which} persists even after accounting for selection effects. Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.

@@

To make substantial progress, it is important to construct statistical high-$z$ samples that reduce the uncertainties, and carefully consider selection effects and inherent systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as a non-gravitational component of the gas dynamics of the broad-line region (BLR), when compared to local samples with masses based on broad Balmer lines~\citep[i.e., \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, measurements of the host galaxy properties are challenging due to the overwhelming glare of the bright nuclear light. This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed QSOs since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}. Especially not to be overlooked as in past studies, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated by~\citet{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in a  \mbh - \smass\ relation with a steeper slope than if chosen randomly, suggesting the selection effects are the culprit rather than an intrinsically faster or even an existing evolution. It is also important to consider the selection function when comparing observed scaling relations with those from simulations \citep{DeG++15}.

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest. In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited. To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic. Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}. This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}.

The paper is organized as follows. We describe the sample selection and their BH masses in Section~\ref{sec:data}. We describe the new HST/WFC3 observations, available HST/ACS imaging, and construction of a PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis}, we describe our method to decompose the rest-frame optical emission and measure the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population from which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations. In addition, we use the information on the radial light distribution (i.e., \sersic\ index) to infer the likely fraction of stars in the bulge (\bmass) and its relation to the \mbh. The discussion and conclusions are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}. Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system. A Chabrier initial mass function (IMF) is employed consistently.

@@

\begin{figure}
\centering
{
\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} Selection window used to choose our AGN sample based on  \mbh~and Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$). As indicated by the vertical red line, our sample (color coded) falls below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. On the right, we illustrate the shape of the Eddington rate distribution at these redshifts from the same reference. For comparison, we plot the high-$z$ luminous SDSS QSO samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
\end{figure}

@@

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling are also provided by this work through a common procedure for spectral model fits. This approach first correct the spectra for galactic extinction and shift to the rest-frame. The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting. The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

@@

To avoid any systematic bias between samples in the literature, we adopt a class of self-consistent estimators for our analysis. We first compare the estimators implemented in \citet{Schulze2018} and \citet{Ding2017b}, and find very consistent \hbeta(FWHM(5100))-based masses (\mbh\ r.m.s. $<0.03$~dex). However, there is a $\sim$0.2 dex inconsistency in their \halpha\ mass estimates. Therefore, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has the best agreement between the two lines. As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta. Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study, including the comparison samples described below.

@@

Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio. To reiterate, an offset in the observed mass relations of 0.2 dex at $z\sim1.5$ can be considered consistent with no evolution in the mass ratio. This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs. Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends. We will revisit these issues in Section~\ref{select_eff}.

@@

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$. In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

@@

%Drizzling, background noise...
For each target, we obtained six separate exposures of 399s (i.e., total exposure time 2394s). The six exposures were dithered and combined with the {\sc astrodrizzle} software package following standard procedures, and resulted in an output pixel scale of 0\farcs{0642} by setting \texttt{pixfrac} parameter as 0.8 and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted. We achieve to analyze this sample using the same approach, taking the 3 available frames.}. In Table~\ref{tab:objlist}, we list the details of the individual observations.

{\bf Obtaining the \hst\ image,  we first account for the background light which could come from both the sky and the detector. In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm. Then, we remove the globe sky background light to obtain the clean image. To ensure the background light has been accurately subtracted, we investigate the surface brightness at the sampled empty area to ensure it is neither positive nor negative.}

We carefully test the surface brightness at the empty area to ensure the

Multi-band information provides the SED at a more precise level. A substantial fraction (21/32) of our objects have rest-frame UV images for those in COSMOS \citep{Koekemoer2007}. Here, we utilize images taken with ACS/F814W filter. The final image is drizzled to 0\farcs{03} pixel scale. Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which ensures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.

@@

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN+host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom). The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects). Note that the 1-D surface brightness profiles are only for illustration purposes. The actual fitting is based on the two-dimensional images. The remaining 31 objects in the sample are shown in Appendix~\ref{sec:restsample}.
}}
\end{figure*}

@@

The host property of an AGN is determined by the following steps. First, we model the AGN and host using each PSF in the library. With the input ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1\sigma$ inference of each parameter is extremely narrow. Thus, we only take the best-fit inference using PSO for further calculations. The errors on the fit parameters are assessed by using different PSFs for each object in the sample.} \citep{PSO}.
To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[0.3,7]$.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best-fit PSFs. We determine the host \sersic\ parameters (i.e., flux, \Reff, \sersic\ index) using a weighted arithmetic mean, calculated as follows:

@@

\begin{figure}
\centering
{
\includegraphics[height=0.25\textwidth]{fig/hist_compare.pdf}
}
\caption{\label{fig:hist_compare} 
Distribution of the host-to-total flux ratio when implementing a different number of top-ranked PSFs.}
\end{figure}

@@

\subsection{Host galaxy properties}
\label{sec:result-hosts}
As shown in Figure~\ref{fig:hist_compare}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$). Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five sample (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.

The distributions of effective radius \Reff\ and \sersic\ index are shown in Figure~\ref{fig:hist_rn}. These values are distributed within the allowed range and not concentrated on either the upper or lower bound. The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc). Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge. Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex). The inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero. This means the size inference of these three systems should really be considered an upper limit, rather than a measurement. However, the inference of their host luminosities and stellar masses are still reliable given the small scatter in the host flux ($<10\%$).

@@

Adopting {\bf the $1$~Gyr and $0.625$~Gyr} stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample{\bf, based on the host inference at WFC3 band}. As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within $0.05$~mag. We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}. $L_R$ ranges between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$) with individual values listed in Table~\ref{tab:result_sersic}.

@@

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}
\caption{\label{fig:ML} 
The {\it observed} black hole mass vs. R-band luminosity relation. The black line and the blue colored equation indicates the best-fit result of the local sample as given in Equation~\ref{eq:MLlocal}, with $1\sigma$ confidence interval indicated by the gray region.
}
\end{figure}

@@

\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z).
\end{eqnarray} 
Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.01 \pm 0.26$ that} may be tentatively considered as evidence for evolution. Even with the exclusion of the few outliers, there is an evolution in the {\bf correlation with $\gamma  = 0.89 \pm 0.27$}. The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.

>>>>

\usepackage{times}
\usepackage{natbib}
\usepackage[backref,breaklinks,colorlinks,citecolor=cyan]{hyperref} 
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{bm}
%\usepackage{deluxetable}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}

@@

Correlations between the mass of a supermassive black hole (SMBH) and the properties of its host galaxy (e.g., stellar mass \smass, luminosity \lhost) suggest an evolutionary connection. A powerful test of a co-evolution scenario is to measure the relations \mbh-\lhost\ and \mbh-\smass~at high redshift and compare with local estimates. For this purpose, we acquired multi-band {\it Hubble Space Telescope} imaging with WFC3 of 32 \hbox{X-ray-selected} broad-line (type-1) AGN at $1.2<z<1.7$ in deep survey fields. By applying state-of-the-art tools to decompose the \hst\ images, we measured the host galaxy luminosity and stellar mass along with other properties through the 2D model fitting. The black hole mass (\mbh) was determined using the broad \halpha~line, detected in the near-infrared with Subaru/FMOS, which potentially minimizes systematic effects using other indicators. We find the {\it observed} ratio of \mbh/\smass~to {\bf be $2.6\times$ larger at $z\sim1.5$ than in} the local universe, while the scatter is equivalent between the two epochs. \ding{(TB update based on Daeseong's result:) an {\it intrinsic} non-evolving mass ratio is consistent with the data at the 95\% confidence level when accounting for selection effects (estimated using two independent and complementary methods).} The relationship between \mbh\ and host galaxy total luminosity paints a similar picture. Therefore, our results are in agreement, considering the uncertainties, with a scenario where SMBHs and their total host stellar mass and luminosity proceed in lockstep or the growth of the former somewhat predates the latter. Based on an inference of the bulge-to-total mass fraction, the ratio \mbh/\bmass~is significantly offset from the local value {\bf by a factor of $+6.8$ which} persists even after accounting for selection effects. Taken together, these observations are consistent with a scenario in which stellar mass is subsequently transferred from an angular momentum supported component of the galaxy to the pressure supported one through secular processes or minor mergers at a faster rate than mass accretion onto the SMBH.

@@

To make substantial progress, it is important to construct statistical high-$z$ samples that reduce the uncertainties, and carefully consider selection effects and inherent systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as a non-gravitational component of the gas dynamics of the broad-line region (BLR), when compared to local samples with masses based on broad Balmer lines~\citep[i.e., \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, measurements of the host galaxy properties are challenging due to the overwhelming glare of the bright nuclear light. This ultimately requires careful modeling of the point spread function and, whenever possible, the use of lensed {\bf AGNs} since the magnification increases the spatial resolution \citep{Pen++06qsob, Ding2017a, Ding2017b}. Especially not to be overlooked as in past studies, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated by~\citet{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in a  \mbh - \smass\ relation with a steeper slope than if chosen randomly, suggesting the selection effects are the culprit rather than an intrinsically faster or even an existing evolution. It is also important to consider the selection function when comparing observed scaling relations with those from simulations \citep{DeG++15}.

In this study, we aim to make progress by utilizing a large sample with high-quality data both for the measurement of the \mbh\ and their host properties, extending to higher redshifts where evolutionary effects should be strongest. In particular, samples based on 2D image analysis using \hst\ at $z>1$ are limited. To date, the infrared capabilities of \hst/WFC3 have not been fully exploited on this topic. Here, we measure the properties of 32 host galaxies within a redshift range of $1.2<z<1.7$ using \hst/WFC3 imaging data, and estimate their \mbh\ based on the robust \halpha\ ~detections, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e., $\sim0.23$ dex,][]{Schulze2014}. This value is the minimum offset expected for a non-evolving mass ratio as described in Section~\ref{sec:sf_framework}. {\bf Furthermore, we collect the most similar AGN sample from the local and intermediate redshift and re-calibrate their quantities based on a set of consistent recipes, which ensures our comparison results solid, see Section~\ref{sec:compare_sample}.}

The paper is organized as follows. We describe the sample selection and their BH masses in Section~\ref{sec:data}. We describe the new \hst/WFC3 observations, available \hst/ACS imaging, and construction of a PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis}, we describe our method to decompose the rest-frame optical emission and measure the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population from which we apply to derive the rest-frame R-band \lhost\,~and \smass\ to compare with local relations. In addition, we use the information on the radial light distribution (i.e., \sersic\ index) to infer the likely fraction of stars in the bulge (\bmass) and its relation to the \mbh. The discussion and conclusions are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}. Throughout this paper, we adopt a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are given in the AB system. A Chabrier initial mass function (IMF) is employed consistently.

@@

\begin{figure}
\centering
{
\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} Selection window used to choose our AGN sample based on  \mbh~and Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$). As indicated by the vertical red line, our sample (color coded) falls below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. On the right, we illustrate the shape of the Eddington rate distribution at these redshifts from the same reference. For comparison, we plot the high-$z$ luminous SDSS {\bf AGN} samples that have been studied with \hst\ ~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}, mainly at the high mass end.}
\end{figure}

@@

The 32 AGNs are initially selected by the X-ray observations of the COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. In most cases, the X-ray sources are first identified as broad-line AGNs through optical spectroscopic campaigns with the VLT, Keck, and Magellan. Follow-up near-infrared spectroscopic observations of the AGNs in these fields are carried out with Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Nobuta2012,Matsuoka2013}, covering the wavelength range $0.9-1.8$~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. Recently, \citet{Schulze2018} present near-IR spectroscopy of a large compilation of 243 X-ray AGN in these fields. It is from this catalog that we primarily select our targets. 
{\bf The continuum fitting and emission-line modeling are also provided by this work through a common procedure for spectral model fits. This approach first correct the spectra for galactic extinction and shift to the rest-frame. The spectral regions in the near-IR were are strongly affected by OH emission, and thus they are masked while fitting. The spectrum are modeled by both a narrow-line and a broad-line AGN template, and the emission line information is inferred based on the $\chi^2$ value. We refer the reader to that paper for more details.}
Note that three CDFS objects (i.e., CDFS-1, CDFS-229 and CDFS-724) are not included in \citet{Schulze2018}; their infrared spectra are provided by \citet{Suh2015} {\bf using a similar approach}.

@@

To avoid any systematic bias between samples in the literature, we adopt a class of self-consistent estimators for our analysis. We first compare the estimators implemented in \citet{Schulze2018} and \citet{Ding2017b}, and find very consistent \hbeta(FWHM(5100))-based masses (\mbh\ r.m.s. $<0.03$~dex). However, there is a $\sim0.2$ dex inconsistency in their \halpha\ mass estimates. Therefore, we utilize the AGNs in \citet{Schulze2018} that have both \halpha\ and \hbeta\ lines (35 AGNs in total) and carry out a cross-calibration to determine which \halpha\ estimator has the best agreement between the two lines. As a  result, the \halpha\ estimator in \citet{Schulze2018} has better agreement with \hbeta. Thus, we adopt the scheme given in \citet{Schulze2018} for all AGN samples used in this study, including the comparison samples described below.

@@

Adopting our specific selection limits into the framework {\bf (i.e., $\log($\mbh$/M_{\odot})\in[7.5, 8.56]$, $\log(L_{\rm bol}/L_{\odot})\in[45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$),} we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$, assuming the baseline choices for the inputs to the model that include the local value of the mass \mbh/\smass ~ratio. To reiterate, an offset in the observed mass relations of 0.2 dex at $z\sim1.5$ can be considered consistent with no evolution in the mass ratio. This bias correction should be considered an approximate estimate, with an uncertainty that depends on the uncertainty of the inputs. Furthermore, if the scaling relations actually evolve, one needs to introduce a model for the evolution in order to infer the underlying bias-corrected trends. We will revisit these issues in Section~\ref{select_eff}.

@@

We include in our analysis published samples at intermediate redshifts to understand the evolution of these correlations. We select samples that were analyzed by members of our team to ensure uniform measurements. The intermediate redshift AGNs that we include are 52 objects published by \citet{Park15} applicable for the \mbh-\lhost\ relation at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11} and \citet{SS13} at $0.5<z<1.9$. {\bf The stellar mass of these 27 object have been estimated using multi-band imaging data, and we adopt them to compare the \mbh-\smass\ relation.}
 In addition, we adopt a sample of 32 \mbh-\smass\ measurements at $0.3<z<0.9$ by \citet{Cisternas2011} to compare with our sample. Across the intermediate redshift sample, we recalibrate the \mbh\ using the self-consistent recipes introduced in Section~\ref{mbh} including those estimated from \Mgii\ using the recipe in \citet{Ding2017b}.

{\bf The value for the all the \mbh-\lhost\ comparison sample are listed in \citet{Ding2017b} (in Table~1 and Table~2). The \mbh-\smass\ comparison sample are collected and summarized in the Appendix~\ref{sec:comp_sample_value}, Table~\ref{tab:comp_sample}.}

@@

%Drizzling, background noise...
For each target, we obtained six separate exposures of $399$s (i.e., total exposure time $2394$s). The six exposures were dithered and combined with the {\sc astrodrizzle} software package following standard procedures, and resulted in an output pixel scale of $0\farcs{0642}$ by setting \texttt{pixfrac} parameter as $0.8$ and using a \texttt{gaussian} kernel\footnote{\label{note1}For CID255, 3/6 of the dither WFC3 images are corrupted. We achieve to analyze this sample using the same approach, taking the 3 available frames.}. In Table~\ref{tab:objlist}, we list the details of the individual observations.

{\bf Having obtained the \hst\ image, we remove the background light which could come from both the sky and the detector. In this step, we adopt the {\sc photutils} by Python and model the global background light in 2D based on the \texttt{SExtractor} algorithm. Then, we subtract the globe sky background light to obtain the clear image. To test the fidelity of this subtraction, we investigate the surface brightness at the empty regions and make sure it is neither positive nor negative. Finally, we extract postage stamp of the AGN image and PSF image to carry out the modeling process, see Section~\ref{sec:psf_library} and Section~\ref{sec:analysis}.}

Multi-band information provides the SED at a more precise level. A substantial fraction (21/32) of our objects have rest-frame UV images for those in COSMOS \citep{Koekemoer2007}. Here, we utilize images taken with ACS/F814W filter. The final image is drizzled to $0\farcs{03}$ pixel scale. Given the multi-band images for our AGN, we are able to infer their host color and assess the contribution of both the young and old stellar population which ensures an accurate inference of rest-frame R-band luminosity (including a K-correction) and stellar mass \citep{Gallazzi2009}.

@@

\begin{figure*}
\centering
%\hspace{-5.5em}
{
\includegraphics[height=0.25\textwidth]{fig/best_fit_CID1174_SB_profile.pdf}
\caption{\label{fig:AGN_decomp} AGN-host galaxy decomposition of COSMOS-CID1174 based on the \hst/WFC3 F140W image.The panels from left to right are as follows: (1) observed data, (2) best-fit model (AGN$+$host), (3) data minus the model PSF (i.e., host galaxy free of the AGN), (4) residuals divided by the variance and (5)~1-D surface brightness profiles (top) and the corresponding residual (bottom). The 1-D profiles indicate the surface brightness including the data (open circles), the best-fit model (blue line), the AGN (orange line), and the model for the extended sources (green line, i.e., host and other objects). Note that the 1-D surface brightness profiles are only for illustration purposes. The actual fitting is based on the two-dimensional images. The remaining 31 objects in the sample are shown in Appendix~\ref{sec:restsample}.
}}
\end{figure*}

@@

The host property of an AGN is determined by the following steps. First, we model the AGN and host using each PSF in the library. With the input ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1\sigma$ inference of each parameter is extremely narrow. Thus, we only take the best-fit inference using PSO for further calculations. The errors on the fit parameters are assessed by using different PSFs for each object in the sample.} \citep{PSO}.
To avoid any unphysical results, we set the upper and lower limits on the parameters: effective radius \Reff~$\in[0\farcs{}1,1\farcs{0}]$, \sersic\ index $n\in[0.3,7]$.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best-fit PSFs. We determine the host \sersic\ parameters (i.e., flux, \Reff, \sersic\ index) using a weighted arithmetic mean, calculated as follows:

@@

\begin{figure}
\centering
{
\includegraphics[height=0.3\textwidth]{fig/hist_f_ratio_compare.pdf}\\
\includegraphics[height=0.3\textwidth]{fig/hist_Reff_compare}\\
}
\caption{\label{fig:hist_compare} 
Distribution of the host-to-total flux ratio {\bf and effective radius} when implementing a different number of top-ranked PSFs.}
\end{figure}

@@

\subsection{Host galaxy properties}
\label{sec:result-hosts}
As shown in Figure~\ref{fig:hist_compare} {\bf (top panel)}, the host-to-total flux ratio (total$=$host$+$nuclear) of the sample spans a wide range from $10\%$ to $90\%$ with most of the sample concentrated between $20\%$ to $50\%$ (median value $37\%$). Those with flux ratios above $\sim20\%$ have a higher degree of significance with respect to the detection of the host galaxy, while the {\bf five sample (i.e., CID255, CID50, LID360, CDFS-229, SXDS-X763) which have host-to-total flux ratios lower than $20\%$} should be considered as marginal detections.

The distributions of effective radius \Reff\ {\bf are shown in Figure~\ref{fig:hist_compare} {\bf (bottom panel)}. Based on the sample redshift and the cosmological model, we calculate their physical scale in kpc unit. We plot them together with inferred \sersic\ index in Figure~\ref{fig:hist_rn}.} These values are distributed within the allowed range and not concentrated on either the upper or lower bound. The \Reff\ of our sample are between $\sim1-7$~kpc (peaked at $\sim2.2$~kpc). Nearly half ($15/32$) of our systems have \sersic\ index $n<2$, indicating they have a significant disk component, likely in addition to the presence of a bulge. Five systems had a high \sersic\ index ($n>4.5$) for the first run; we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex). 
{\bf Seven systems have low effective radius \Reff$<0\farcs18$ that is within 3 pixels; we re-fit them with a \Reff\ $\in[0\farcs{}2,1\farcs{0}]$ prior and find that the inferred host flux barely changes ($<1\%$). In particular, the}
inferred \Reff\ for systems (CID543, XID2202, and SXDS-X1136) have hit the lower limit (i.e., $0\farcs{}1$), and thus the scatter on the parameter is formally zero. This means the size inference of these three systems should really be considered an upper limit, rather than a measurement. However, the inference of their host luminosities and stellar masses are still reliable given {\bf the consistent result of our re-fitting test and} the small scatter in the host flux ($<10\%$).

@@

Adopting {\bf the $1$~Gyr and $0.625$~Gyr} stellar population, we perform a K-correction to derive the rest-frame R-band magnitude of our sample{\bf, based on the host inference at WFC3 band}. As mentioned above, since the WFC3 filter is already close to the rest-frame R-band, we expect the $M_R$ uncertainty introduced by this K-correction to be within $0.05$~mag. We derive the rest-frame R band luminosity from $\log L_R/L_{R, \odot} = 0.4\times(M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}. $L_R$ ranges {\bf between $\log (L_R/L_{\odot,R})  \in [9.5, 11.5]$ with} individual values listed in Table~\ref{tab:result_sersic}.

@@

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-L_obs.pdf}}
\caption{\label{fig:ML} 
The {\it observed} black hole mass vs. R-band luminosity relation. The black line and the blue colored equation indicates the best-fit result of the local sample as given in Equation~\ref{eq:MLlocal}, with $1\sigma$ confidence interval indicated by the gray region. {\bf The values for the comparison sample, including the local and the intermediate, are listed in \citet{Ding2017b}, Table 1 and 2.}
}
\end{figure}

@@

\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z).
\end{eqnarray} 
Performing such a fit based on the {\it observed} data (i.e., no correction for selection effects), {\bf we obtain $\gamma  = 1.03 \pm 0.25$ that} may be tentatively considered as evidence for evolution. Even with the exclusion of the few outliers, there is an evolution in the {\bf correlation with $\gamma  = 0.89 \pm 0.27$}. The best-fit {\it observed} evolution model is shown in Figure~\ref{fig:MM-vz}.
